Should geophysicists use the gravity disturbance or the anomaly?

### 2018-05-22 manuscript/letter.tex

\begin{figure}
    \includegraphics{figures/surfaces.png}
    \caption{
    The gravity vector
    $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
    gravity disturbance vector $\delta \vector{g}_{P}$
    (eq. \ref{eq:gravity-disturbance-vector}), and unit vector
    $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point $P$
    on the surface of the Earth.
    The gravity vector $\vector{g}_{Q^{\prime}}$
    at a point $Q^{\prime}$ on the geoid, normal gravity vector
    $\vector{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
    geometric height $h$, orthometric height $H$, and geoidal height $N$.
    The dashed line passing through
    $Q$, $Q^{\prime}$ and $P$ is normal to the
    surface of the reference ellipsoid at $Q$.
    This figure shows a commonly used approximation in which the ellipsoid and
    geoid are represented as parallel surfaces so that $h \approx H + N$.
    }
  \label{fig:surfaces}
\end{figure}

@@

We know empirically that $N$ is $\approx \pm 1$ m on the oceans
and reaches a maximum absolute value of $\approx 120$ m
\citep[e.g.,][]{torge2012, sanso_sideris2013}.
In Brazil, for example, the geoidal height
varies between $\approx \pm 30$ m \citep{ibge_mapgeo2015}.
Consequently,
the maximum absolute difference between the gravity disturbance and
the free-air anomaly in Brazil,
according to eq. \ref{eq:difference-disturbance-free-air},
is $\approx 9.258$ mGal.

>>>>

\begin{figure}
    \includegraphics{figures/surfaces.eps}
    \caption{
    The gravity vector
    $\vector{g}_{P}$, normal gravity vector $\vector{\gamma}_{P}$,
    gravity disturbance vector $\delta \vector{g}_{P}$
    (eq. \ref{eq:gravity-disturbance-vector}), and unit vector
    $\versor{u}_{P}$ (eq. \ref{eq:unit-vectors}) at a point $P$
    on the surface of the Earth.
    The gravity vector $\vector{g}_{Q^{\prime}}$
    at a point $Q^{\prime}$ on the geoid, normal gravity vector
    $\vector{\gamma}_{Q}$ at a point $Q$ on the reference ellipsoid,
    geometric height $h$, orthometric height $H$, and geoidal height $N$.
    The dashed line passing through
    $Q$, $Q^{\prime}$ and $P$ is normal to the
    surface of the reference ellipsoid at $Q$.
    This figure shows a commonly used approximation in which the ellipsoid and
    geoid are represented as parallel surfaces so that $h \approx H + N$.
    }
  \label{fig:surfaces}
\end{figure}

@@

We know empirically that $N$ is $\approx \pm 1$ m on the oceans
and reaches a maximum absolute value of $\approx 120$ m
\citep[e.g.,][]{torge2012, sanso_sideris2013}.
Fig. \ref{fig:difference} shows the absolute difference between the
gravity disturbance and the free-anomaly globally calculated
using eq. \ref{eq:difference-disturbance-free-air} and the spherical harmonic
model EIGEN-6c4 \citep{forste2014}.
In Brazil, for example, the geoidal height
varies between $\approx \pm 30$ m \citep{ibge_mapgeo2015}.
Consequently,
the maximum absolute difference between the gravity disturbance and
the free-air anomaly in Brazil,
according to eq. \ref{eq:difference-disturbance-free-air},
is $\approx 9.258$ mGal.

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/difference.eps}
    \caption{
    Absolute difference between the gravity disturbance and free-air anomaly.
    Calculated using eq. \ref{eq:difference-disturbance-free-air}, the
    EIGEN-6c4 \citep{forste2014} spherical harmonic model, and software
    \textit{Fatiando a Terra} \citep{uieda2013}. The figure was made using GMT
    \citep{wessel2013}.
    }
  \label{fig:difference}
\end{figure}
